Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants\thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN 712689 SC$^2$.}

### 2017-04-29 cav2017/cav2017.tex
missing article

We provide experimental results showing that both approaches are able to
efficiently synthesize stable and safe controllers for a set of intricate
physical plant models taken from the digital control literature: the median
run-time for our benchmark set is $7.9$ seconds, and most controllers can be
synthesized in less than $17.2$ seconds.  We further show that, in a direct
comparison, the abstraction-based approach (i.e., second approach) lowers the median
run-time of our benchmarks by a factor of seven over the first approach
based on the unfolding of the dynamics.

>>>>

We provide experimental results showing that both approaches are able to
efficiently synthesize stable and safe controllers for a set of intricate
physical plant models taken from the digital control literature: the median
run-time for our benchmark set is $7.9$ seconds, and most controllers can be
synthesized in less than $17.2$ seconds.  We further show that, in a direct
comparison, the abstraction-based approach (i.e., the second approach) lowers the median
run-time of our benchmarks by a factor of seven over the first approach
based on the unfolding of the dynamics.
